Pre/Post-Trikafta

### 2022-01-13 Christine Chan/Pre-post Trikafta/pre_post_trikafta.Rmd
Update pre_post_trikafta.Rmd

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Christine Chan/Prepost Triakfta")
```

```{r import}
cgm_c <- read.csv("./Data_Raw/Data From CHCO/REDCap Upload_chco.csv")
```

>>>>

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(readxl)
library(PAutilities)
library(AGD)
library(rspiro)
library(anthro)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Christine Chan/Prepost Triakfta")
```

```{r code from maxie,eval=FALSE}
# Source Maxie's code, and write final ID lists
source("~/GitHub/CF/Christine Chan/Pre-post Trikafta/p001+cmw_UPDATED.R")
ids = data.frame(unique(analytic_cm$CFF.ID))
colnames(ids) = "CFF.ID"
write.csv(ids,file = "./Data_Cleaned/final_ids.csv",row.names = F)
```

# Table 1: Demographics at Trikafta Start

```{r}
# Start dates
chco_dates = read.csv("./Data_Cleaned/chco_trikafta_dates.csv")
# Fix select dates
chco_dates$Earliest.Trikafta.Date.in.PortCF[chco_dates$MRN =="1053930"] = "12/1/2019"
chco_dates$Earliest.Trikafta.Date.in.PortCF[chco_dates$MRN =="1695512"] = "12/12/2019"
chco_dates$Earliest.Trikafta.Date.in.PortCF[chco_dates$MRN =="815274"] = "12/13/2019"
chco_dates$Earliest.Trikafta.Date.in.PortCF[chco_dates$MRN =="1078408"] = "3/9/2020"
chco_dates$Earliest.Trikafta.Date.in.PortCF[chco_dates$MRN =="899717"] = "2/14/2020"
chco_dates$CFF.ID = as.character(chco_dates$CFF.ID)
# A1C and OGTT
chco_a1c = read.csv("./Data_Cleaned/chco_a1c_ogtt.csv")
chco_a1c$CFF.ID = as.character(chco_a1c$CFF.ID)
chco_pft = read.csv("./Data_Cleaned/chco_bmi_pft.csv")
# Merge
chco = left_join(chco_dates,chco_a1c,by = "CFF.ID")
chco = full_join(chco,chco_pft,by = c("MRN", "Date"))
# Diabetes only
chco = chco %>% filter(!is.na(Diabetes)) %>% mutate(Location = "CHCO")
# Montana
montana = read.csv("./Data_Raw/Data From Montana/Copy of Paper patient population glycemic (+hofer).csv")
demo_adult <- read.csv("./Data_Raw/Data From Montana/demo_adults.csv")
demo_kids <- read.csv("./Data_Raw/Data From Montana/demo_kids.csv")
montana
```

```{r cgm data,eval=FALSE}
# IDs from Maxie
ids = read.csv("./Data_Cleaned/final_ids.csv")
# CGM
chco_cgm = read.csv("./Data_Cleaned/chco_cgm.csv")
chco_cgm$timepoint = sub(".*_","",chco_cgm$subject_id)
chco_cgm$timepoint = factor(chco_cgm$timepoint)
levels(chco_cgm$timepoint) = c("Post","Post","Pre","Pre")
chco_cgm$subject_id = sub("_.*","",chco_cgm$subject_id)
colnames(chco_cgm)[which(colnames(chco_cgm) == "subject_id")] = "CFF.ID"
# First visit post if more than 1, and only those with pre and post
chco_cgm = chco_cgm %>% group_by(CFF.ID,timepoint) %>%
  slice(which.min(as.Date(date_cgm_placement, '%m/%d/%Y %H:%M')))

# Put everything together
chco = left_join(chco_cgm,chco_dates)

chco = full_join(chco_dates,chco_a1c,by = "CFF.ID")
chco = full_join(chco,chco_pft,by = c("MRN", "Date"))
chco = full_join(chco,chco_cgm,by = c("CFF.ID", "Date"))
# Filter and select columns
chco = chco %>% filter(CFF.ID %in% ids$CFF.ID)
```

```{r montana data}

```
